---
title: "Report Ebola"
author: "Nicole Schönenberger"
date: "`r date()"
format:
  html:
    toc: true
    code-fold: show
    df-print: paged
    embed-resources: true
---


```{r}
#\| output: false
#Load libraries
library(here)
library(tidyverse)
library(lubridate)
```

## Introduction

The aim of this exercise is to visualize the increase of confirmed cases of Ebola in Spain, Liberia, and Sierra Leone.

## Data

```{r}
#| output: false
# Read data
dat <- read_csv("~/Documents/PhD/Basics in Statistics and R/Excercise01/data/raw/ebola.csv")

#Sort data
dat_before <- dat |> filter(Date < "2015-04-01") #Filter by dates before 31.03.2015

dat_countries <- dat_before |> filter(Country %in% c("Spain", "Sierra Leone", "Liberia"))
```

## Results

@fig-cases shows the number of confirmed cases of Ebola in Liberia, Spain, and Sierra Leone

```{r}
#| label: fig-cases
#| fig-cap: "Confirmed cases of Ebola in Liberia, Spain, and Sierra Leone"
#| fig-width: 8
#| fig-height: 4
ggplot(data = dat_countries, 
                               mapping = aes(x = Date, y = Cum_conf_cases, fill = Country, colour = Country)) + 
  geom_point(alpha = 0.7, shape = 21, size = 1.5, stroke = 1.5) +
  scale_fill_manual(name = "Country",
                    breaks = c("Liberia", "Sierra Leone", "Spain"),
                    values = c("red", "purple","navy"),
                    labels = c("Liberia", "Sierra Leone", "Spain")) +
  scale_colour_manual(name = "Country",
                      breaks = c("Liberia", "Sierra Leone", "Spain"),
                      values = c("red", "purple", "navy"),
                      labels = c("Liberia", "Sierra Leone", "Spain")) +
  scale_x_date(breaks = as.Date(c("2014-08-29", "2014-10-01", "2014-12-01", "2015-02-01", 
                                  "2015-04-01")),
               labels = c("29 August", "1 October", "1 December", "1 February", "1 April"),
               limits = as.Date(c("2014-08-29", "2015-04-01"))) +
  scale_y_continuous(breaks = seq(from = 0, to = 10000, by = 2000),
                     limits = c(0, 10000)) +
  ggtitle(label = "Confirmed ebola cases") +
  xlab(label = "Time") +
  ylab(label = "Cum. # of confirmed cases") +
  theme_bw() + theme(legend.position="bottom")
```

## Conclusions

The number of confirmed Ebola and in Spain are low, whereas Libera and Sierra Leone showed a steeo increase in confirmed cases.
